|

### 2022-02-24 paper/dcpo_demsupport.Rmd
update dcpo

- Yuehong 'Cassandra' Tai, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
- Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu."

@@

```{r dcpo-AJPS, eval=FALSE}
dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
    dcpo_ajps[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year")) %>%
        rename(
            SupDem_trim = theta_trim,
            Regime_VD = Vdem_regime,
            Pr_Muslim = muslism_prop_2010,
            Res_cp_WDI_di = dependence_pc_di,
            lnGDP_imp = lg_imp_mdpgdp,
            GDP_imp_grth = mdprgdp_grwth,
            firstyear = first_year,
            Libdem_VD = Vdem_libdem,
            Libdem_m1 = Vdem_libdem_m1,
            Libdem_m2 = Vdem_libdem_m2,
            ChgDem = Chgdem,
            UpChgDem = upchgdem,
            DwnChgDem = downchgdem,
            Libdem_regUN = Region_libdem,
            Libdem_regUN_m1 = Region_libdem_m1
        )
})

@@

```{r dcpo-APSR, eval=FALSE}
dcpo_APSR <- purrr::map(1:900, function(anEntry) {
    dcpo_apsr[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year")) %>%
        rename(
            SupDem_trim = theta_trim,
            First_yr = first_year,
            Libdem_z = Vdem_libdem_z,
            Polyarchy_z = Vdem_polyarchy_z,
            Liberal_z = Vdem_liberal_z,
            Corrup_TI_z = corruption_z,
            lnGDP_imp = lg_imp_mdpgdp
        )
})

>>>>

- Yuehong 'Cassandra' Tai, ORCID: https://orcid.org/0000-0001-7303-7443, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
- Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu."

@@

```{r dcpodata-input, include=FALSE}
## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download

mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <-
    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
```

```{r dcpo-AJPS, eval=FALSE}
dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
    dcpo_ajps[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year")) 
})

@@

```{r dcpo-APSR, eval=FALSE}
dcpo_APSR <- purrr::map(1:900, function(anEntry) {
    dcpo_apsr[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year")) 
})
